Compare pseqs

### 2019-05-28 comparepseqs.Rmd
DEbug line removed
Minor

```{r rds subset, eval = FALSE}
subset.run <- 3
```

```{r rds files}
rds <- list("shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs",
            "gtdb" = "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
            "ncbi" = "data/phfinrisk_custom70_species_all_2019-01-29.RDs",
            "R16S" = "data/phfinrisk_16S_otu_raw_2019-02-19.RDs")
```

```{r subset runs}
if (exists("subset.run")) {
    message(sprintf("Subset %s of %s", subset.run, rds[[subset.run]]))
    rds <- rds[subset.run]
}

rds <- list("gtdb" = 1 , "centrifuge" = 2, "ncbi" = 3)
```

@@

```{r plot, eval = FALSE}
plotlist <- list()

@@

    alpha.diversity.min <- plot.alpha(diversities$min, alphabreaks = c(-0.15, -0.10, -0.05, 0))
    alpha.diversity.full <- plot.alpha(diversities$full, alphabreaks = c(-0.15, -0.10, -0.05, -0))

@@

    ggsave(file = paste0("cache/alpha-beta-", key , ".png"), plot=g4, height=6, width=9)
    plotlist[[key]] = g4
}
```

```{r plot alpha diversity, eval = FALSE}
g <- arrangeGrob(grobs = plotlist, ncol=2)
ggsave(file="cache/plotlist.pdf", g, height=6*length(plotlist)/1.5, width=10*2)
```

@@

>>>>

```{r rds subset, eval = FALSE}
esubset.run <- 3
```

```{r rds files}
rds <- list("shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs",
            "gtdb" = "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
            "ncbi" = "data/phfinrisk_custom70_species_all_2019-01-29.RDs")
#            "R16S" = "data/phfinrisk_16S_otu_raw_2019-02-19.RDs")
```

```{r subset runs}
if (exists("subset.run")) {
    message(sprintf("Subset %s of %s", subset.run, rds[[subset.run]]))
    rds <- rds[subset.run]
}
```

@@

```{r plot, eval = FALSE}
if (!exists("subset.run")) {
    plotlist <- list()

@@

        alpha.diversity.min <- plot.alpha(diversities$min, alphabreaks = c(-0.15, -0.10, -0.05, -0.01, 0))
        alpha.diversity.full <- plot.alpha(diversities$full, alphabreaks = c(-0.15, -0.10, -0.05, -0.01, -0))

@@

        ggsave(file = paste0("cache/alpha-beta-", key , ".png"), plot=g4, height=6, width=9)
        plotlist[[key]] = g4
    }

    g <- arrangeGrob(grobs = plotlist, ncol=2)
    ggsave(file="cache/plotlist.png", g, height=6*length(plotlist)/1.5, width=10*2)
} else {
    message("Skipping graphics")
}
```

@@

```{r debug alpha, eval = FALSE}
alphadiversity <- readRDS(file = paste0("rds-comparepseqs/alpha-R16S.rds"))
alphadiversity

```

Full model R2

```{r diff beta debug, eval = FALSE}
betadf <- data.frame()
for (key in names(rds)) {
    moddf.full <- Reduce(function(...) merge(..., all=T), ret[[key]][["betadiversity"]]$full) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "full") %>%
        select(term, model, covariates, R2)
    moddf.min <- Reduce(function(...) merge(..., all=T), ret[[key]][["betadiversity"]]$min) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "min") %>%
        select(term, model, covariates, R2)
    betadf <- rbind(betadf, moddf.full, moddf.min)
}

betadf %>% arrange(term) %>% spread(model, R2) %>% kable
```

```{r debugging adonis, eval = FALSE}
pseq <- import_filter_data(rds[["gtdb"]])

bray.dist.matrix <- readRDS(file = paste0("rds-comparepseqs/bray-gtdb.rds"))

dset.sample <- dset %>% sample_n(50)

dset.ids <- dset.sample %>% pull(Sample_ID)

betadiversity <- list(min = calculateadonis(dset = dset.sample,
                                            matrix = bray.dist.matrix[dset.ids, dset.ids],
                                            covariates = covariates.min,
                                            npermutations = 10000),
                      full = calculateadonis(dset = dset.sample,
                                      matrix = bray.dist.matrix[dset.ids, dset.ids],
                                      covariates = covariates.full,
                                      npermutations = 2))

betadiversity$full

betadf <- data.frame()
for (key in names(rds)) {
    moddf.full <- Reduce(function(...) merge(..., all=T), betadiversity$full) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "full") %>%
        select(term, model, covariates, R2)
    moddf.min <- Reduce(function(...) merge(..., all=T), betadiversity$min) %>%
        dplyr::filter(response == term) %>%
        mutate(model = key, covariates = "min") %>%
        select(term, model, covariates, R2)
    betadf <- rbind(betadf, moddf.full, moddf.min)
}
betadf %>% arrange(term) %>% spread(model, R2) %>% kable

```
